### 2019-07-17 manuscript/response.tex

\begin{quote}
--140 I lost track a little of how the data were coded -- maybe add an explicit statement as to how many tips had both forms of data, how many had only breeding system info, how many had only ploidy info (I see now, after the fact, that those data are included in the figure), and how missing data were handled
\end{quote}

Added.

\begin{quote}
--It's not intuitive to me what the effects of forcing the hidden state change rates to be symmetrical are.
Did the authors investigate this?
Or has it been explored in the literature?
Similarly, it seems to me that fixing the transition rates of the observed characters to be independent of the hidden state could do weird things---the point of these SSE models is that state change rates and state-dependent diversification rates need to be co-estimated
\end{quote}

We appreciate this suggestion and we followed it. The main result after fitting models with symmetric vs. asymmetric rates is that the direction of the results does not change but the amount of difference amongst net diversification posterior distributions does. 
We found using Bayes factors that a model including asymmetric hidden rates is preferred over a model with equal hidden rates (Table S6, Figure S5). 
Also,  the asymmetry in the trait rates have moderate to not support of being better than a model with equal trait transition rates.

@@

\begin{quote}
--340  Sentence fragment
\end{quote}

Fixed.

\begin{quote}
--beginning of the Discussion is perhaps unnecessary -- it's more like Introduction material
\end{quote}

The discussion was heavily edited. However, we consider that it is important to refresh some of the introductory key points due to the numerous and complex questions that are being addressed with SSE models. 
 % TODO %We can defend this on account of repeating some of the points because of numerous and complex  questions; aimed to prevent flipping pages back
% Fixed

@@

\begin{quote}
--are the results from the analyses that include diploidization coherent?
I'm not sure how to phrase this -- I guess I'm asking if there's any suggestion that that parameterization is indeed capturing the biological phenomenon of diploidization, or is it just soaking up noise?
\end{quote}

%B: Rosana, you know this best, but it seems to me that the current phrasing (below) is unclear.
%R- rewritten
The soaking noise comes from adding  hidden states to models. Therefore in the presence of hidden states finding that diploidization  parameter is different from zero truly represents potential evidence of the reversibility of polyploidy. 
Furthermore, all the Bayes factors indicated strong preference for models that include diploidization. 
However, diploidization is a genomic process that can be partially or minimally recover from ploidy data. 
And as discussed at the end of the article, genomic evidence for diploidization in Solanaceae  is still debatable.

@@

\begin{quote}
--410  ``as self-incompatibility loci''?
\end{quote}

Fixed.

\begin{quote}
--417  Why would the rates for diploids be inflated?
So the diploids were ancestrally polyploidy -- why would that alter the rate inferences?
\end{quote}

We edited the discussion. We found not evidence of conclusions about diversification changing in the presence of diploidization. The  the estimates for rate of polyploidization in the absence of diploidization also remained the same (\cref{figure:hissedip}. However, ignoring diploidization, if it is common, could cause to underestimate the polyploidization rate or create larger credible intervals.

We have corrected the phrase accordingly.
Thank you for the suggestion
\begin{figure}
    \centering 
      \begin{minipage}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{hisseDPnodipasymposteriordist.pdf} 
    \end{minipage}\\
    \vspace{1cm}
    \begin{minipage}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{hisseDPasymposteriordist.pdf}
        \end{minipage}
    \caption{ Top 6 panels: Ploidy model with hidden states without diploidization. Bottom 6 panels: Ploidy model with hidden states with diploidization. Rate of polyploidy has a wider credible interval in the absence of diploidization}
    \label{figure:hissedip}
\end{figure}

\begin{quote}1
--430  remove the comma
\end{quote}

@@

We have rewritten parts of the manuscript, especially in the Introduction, to try to explain better the relationship between polyploidy and self-incompatibility, and the interpretations of hidden state models.
% E: I labeled the two paragraphs that I modified heavily.

\begin{quote}
My second comment has to do with the parameterization of the models.
Overall, I think that the authors have done a great job in justifying their models and explaining them.
I think it is important to mention.
In addition, their implementation of the models in revBayes is noteworthy and although not stated precisely in the manuscript, I believe this represents a great scientific contribution. 
Nevertheless, I question the decision to restrict the transition rates to and from the hidden states to be all equal.
Indeed, we have no idea that could make us think that this would be the case.
The authors justify this by ``Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fit a simplified version with 16 parameters.''
I am not completely convinced by this argument.
First, constraining transition rates can have an impact on the estimation of diversification rates.
Second, specifically because the authors are not interested in estimating the rates themselves, they should not be too worried about increasing the number of parameters.
This is especially true in a Bayesian framework where it is sometimes better to have overparameterized models than under-parameterized models (see Lemmon and Moriarty. 2004. Systematic Biology 53:265–277).
I think it would have been important to at least present the results of an unconstrained model to show that this decision to constrain the rates do not affect the conclusions.
\end{quote}

We have now fitted models with asymmetric hidden rates and asymmetric trait rates. We found that the former are important and strengthened the differences. We found no evidence that having all asymmetric rates is preferable over just asymmetric hidden for our specific example (Figure S5, Table S6).

@@

\begin{quote}
Finally, I have a suggestion for the authors.
One thing that I would have like to see is a discussion regarding the distribution of the hidden states at the tip of the tree (e.g., Fig S6, S8).
The two peaks distributions obtained for the hidden and non-hidden states made me wonder if the high and low rate peaks could be restricted to specific clades on the phylogeny.
After inspecting the supplementary material, I see that it is not the case; hidden states are rather spread throughout the phylogeny.
I think this is interesting and that it could make an interesting discussion.
\end{quote}

Thank you for this suggestion. Fitting the new models the only trend we can notice is that for ploidy only models hidden states seem to transition mostly towards recent lineages but still spread throughout lineages (Figure S8). For breeding system models there are a two or three clades where transitions between hidden states happen sooner (Figure S12 and S16). However, we don't have a clear interpretation for this phenomenon.

@@

\begin{quote}
Line 392: ``our findings suggest that the effect of ploidy''.
Add ``on diversification rates'' after these words?
\end{quote}

Fixed.

\begin{quote}
Line 416: ``Unduly ignoring secondary diploidization would necessarily underestimate the rate of transitions from polyploids to diploids.''
Actually, if I understand well, models without diploidization simply fix this rate of transition from polyploidy to diploids at 0.
Am I right?
\end{quote}

Correct, and inference remains the same. \cref{figure:hissedip}. However, ignoring diploidization, if it is common, could cause to underestimate the polyploidization rate or create larger credible intervals.
We have corrected the phrase accordingly.

@@

I have a few comments that I hope the authors will find useful.
\end{quote}

We appreciate this positive summary.

\begin{quote}
The first relates to the use of the hidden states in the models.
I agree completely with the rationale and meaning of including hidden states.
However, through my reading of the manuscript, I interpret the authors as using them simply to account for variation within a particular character state combination.
In other words, the authors are working under an assumption of trait-dependent diversification, with the hidden states simply providing a more nuanced view of the process.
But the authors are not considering a completely alternative view, which is that none of these trait combinations are strong drivers of diversification and that the shifts being inferred are simply coincidental.
Such an interpretation could be ruled out by explicitly fitting a model of trait-independent diversification.
This is achieved by linking the diversification rate parameters among the different character state combinations -- i.e., $ID_A=CD_A=CP_A$, and $ID_B=CD_B=CP_B$.
In other words, because the diversification rate differences are completely linked among the possible states, but unlinked by the hidden states, this forces an explicitly trait-independent model.
The fit of such a model could be included in the set of models in Table 1 and compared using Bayes Factors.
Of course, admittedly, I am not familiar with revBayes and how the model space is set up, so it's possible this issue is already being addressed.
But, if so, some clarity in the Methods/Results is warranted in how trait-independent models were evaluated (or even ruled out) in the analyses presented.
\end{quote}

We have fitted the trait independent models (character-independent CID). 
We appreciated this suggestion because it allowed us to parse out the effect of the traits in the diversification process. 
By comparing Bayes factors, models with traits are strongly preferred over CID when the breeding system is the focal trait, and there is little to no evidence that models that include ploidy are better than CID (Tables 1-2 and S1-S3). 
These results strongly suggest that breeding system is much more informative than ploidy in the diversification dynamics of Solanaceae (Tables 1-2).
%TODO: write table number- Fixed

@@

\begin{quote}
Along these same lines, how does revBayes deal with the symmetry problem with regards to the hidden states?
For example, imagine for one sample in the chain the speciation rate for $CP_A=0.1$ and $CP_B=0.05$, all else being equal.
Now, imagine in another sample the speciation rate parameters are exactly the same, but this time $CP_A=0.05$ and $CP_B=0.1$. 
Strangely, this would produce an identical likelihood as the previous sample (again, all else being equal), because A and B are really interchangeable.
This would, however, cause issues with how the posterior is summarized.
I should point out that nothing in the plots suggests this might be an issue, but this was something that I wondered about with the particular models used here.
\end{quote}

When we presented the first submission we were pushing the limits on implementations of diversification models in RevBayes. During the revision we found a work-around to be able to implement all the extra models we are presenting. New models with asymmetric traits are preferred and strengthen the results (Figure S5, Table S6).

### 2019-07-17 manuscript/discussion.tex
Fixed all response to reviews

Polyploidization is known to be common in plants, but the relative frequency of the reverse process---diploidization---remains unclear, and it is under active investigation \citep{dodsworth_2015,mandakova_2018}.
%
Ignoring diploidization, if it is common, could cause us to both underestimate the polyploidization rate and overestimate of the diploid diversification rate, leading to incorrect conclusions.
Therefore, we included a slate of models with a diploidization parameter, and show that our main conclusions are robust to this process (\cref{suppfigure:alldip}).
These models also suggest modest statistical support for diploidization (\cref{supptable:testdiploidization}), although our estimates of its rate were highly uncertain. 
Furthermore, additional lines of evidence for classifying species as diploid or polyploid (beyond the genus-level chromosome multiplicity that we primarily relied on) are needed for more reliable conclusions.
%In the cases where ploidy level was assigned by us based chromosome multiplicity at the genus level, estimating diploidization might be a potential issue due to ploidy misclassification.  
%R: By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with comparative phylogenetic models. 
%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.

>>>>

Polyploidization is known to be common in plants, but the relative frequency of the reverse process---diploidization---remains unclear, and it is under active investigation \citep{dodsworth_2015,mandakova_2018}.
%
Ignoring diploidization, if it is common, could cause underestimation and increase of uncertainty in  the polyploidization rate. 
Therefore, we included a slate of models with a diploidization parameter, and show that our main conclusions are robust to this process (\cref{suppfigure:alldip}).
These models also suggest modest statistical support for diploidization (\cref{supptable:testdiploidization}), although our estimates of its rate were highly uncertain. 
Furthermore, additional lines of evidence for classifying species as diploid or polyploid (beyond the genus-level chromosome multiplicity that we primarily relied on) are needed for more reliable conclusions.
%In the cases where ploidy level was assigned by us based chromosome multiplicity at the genus level, estimating diploidization might be a potential issue due to ploidy misclassification.  
%R: By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with comparative phylogenetic models. 
%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.
